Manuscript 1 code

### 2025-01-24 manuscript_1_code.Rmd
starting to add cover as area calculations

# write_csv(macro_long_data, here("Data", "macro_long_data.csv"))
```

```{r site macroalgal data}
site_macro <- macroalgae %>%
  dplyr::group_by(year, site, habitat,site_habitat) %>%
  dplyr::summarize(across(acanthophora_spicifera:valonia_ventricosa, \(x) mean(x, na.rm = TRUE)))

@@

alpha_diversity_quad_macro <-
  left_join(alpha_diversity_quad_macro, macroalgal_cover_quad,by = join_by(location, year, site, habitat)) %>% 
  mutate(macroalgal_prop_cover = macroalgae / 100) %>% 
  select(-macroalgae)
```

@@

alpha_diversity_site_macro$cover_trans <- sv_trans(alpha_diversity_site_macro$prop_cover)
```

>>>>

# convert cover to area
macro_long_data$area <- macro_long_data$prop_cover*0.25
# write_csv(macro_long_data, here("Data", "macro_long_data.csv"))
```

```{r site macroalgal data}
# NOTE - FRI JAN 24 - updated mean() in summarize across to sum() to reflect new method of calculating cover as area
site_macro <- macroalgae %>%
  dplyr::group_by(year, site, habitat,site_habitat) %>%
  dplyr::summarize(across(acanthophora_spicifera:valonia_ventricosa, \(x) sum(x, na.rm = TRUE)))

@@

alpha_diversity_quad_macro <-
  left_join(alpha_diversity_quad_macro, macroalgal_cover_quad,by = join_by(location, year, site, habitat)) %>% 
  mutate(macroalgal_prop_cover = macroalgae / 100) %>% 
  select(-macroalgae)

alpha_diversity_quad_macro$area <- alpha_diversity_quad_macro$macroalgal_prop_cover*0.25
```

@@

alpha_diversity_site_macro$cover_trans <- sv_trans(alpha_diversity_site_macro$prop_cover)

alpha_diversity_site_macro$area <- alpha_diversity_site_macro$prop_cover*0.25
```
